---
title: "Credit Card Clients Analysis(Decision Tree)"
output: html_notebook
---

This command is used to view the Original DataSet
```{r}
View(default_of_credit_card_clients)
```

The orginal dataset is being duplicated into another document before further analysis.
```{r}
credit_clients2=default_of_credit_card_clients
```

The Structure of the duplicated Dataset is Viewed using this function
```{r}
str(credit_clients2)
```

The Summary of the Dataset is derived using this function
```{r}
summary(credit_clients2)
```

Using caTools Library, we factorize the dependent variable(dpnm) and education,SampleSplit(sample_cc)with a Ratio(0.8),Train(train_cc)and Test(test_cc) the Dataset.
```{r}
library(caTools)
credit_clients2$dpnm=factor(credit_clients2$dpnm,levels = c(0,1))
credit_clients2$EDUCATION=factor(credit_clients2$EDUCATION,levels = c(1,2,3,4,5,6))
sample_cc=sample.split(credit_clients2,SplitRatio = 0.8)
sample_cc
train_cc=subset(credit_clients2,sample_cc=="TRUE")
train_cc
test_cc=subset(credit_clients2,sample_cc=="FALSE")
test_cc
```

Post the Train and Test Process of the dataset,we use (rpart) and (rpart.plot) library to derive the decision tree for the test data that is assigned.
We use rpart.control function to control the Decision Tree limits.
We use Printcp,Plotcp function to rectify if there were any overfit in the derived decision tree.
```{r}
library(rpart)
library(rpart.plot)
my_cc_model1=rpart.control(minsplit = 6,minbucket = round(5/3),maxdepth = 6,cp = 0)
my_cc_model=rpart(dpnm~.,data = test_cc,method = "class",
                  control =my_cc_model1)
my_cc_model
rpart.plot(my_cc_model)
printcp(my_cc_model)
plotcp(my_cc_model)
```

After deriving the Decision Tree,We Predict The Values of Test data.
Then,we use table function to derive the Actual Value of the Dependent Variable(dpnm) from the dataset and the Predicted value of the using the test dataset.
```{r}
pred=predict(my_cc_model,test_cc,type = "class")
pred
t1=table(actualvalue=test_cc$dpnm,predictedvalue=pred)
```

Finally,We conclude by checking the accuracy of the Predicted Value with the Actual Value.
Here,the Accuracy of the Predicted value =0.8388 (i.e) 83.88%
```{r}
accu_test=sum(diag(t1))/sum(t1)
accu_test

```


