---
title: "Logistic Regression-R Dec Evaluation"
output:
  html_notebook: default
  pdf_document: default
---
Viewing,Creating a new duplicate dataset for analysis,Viewing the Structure,Summary of the duplicated dataset.
```{r}
View(Titanic)
Titaniclog1=Titanic
str(Titaniclog1)
summary(Titaniclog1)
View(Titaniclog1)
```

Removing NA values,Converting Age Variable as numeric and assigning the missing age variables by using mean method.
```{r}
Titaniclog1=na.omit(Titaniclog1)
Titaniclog1$Age=as.numeric(Titaniclog1$Age) 
Titaniclog1$Age[is.na(Titaniclog1$Age)]=mean(Titaniclog1$Age,na.rm = TRUE)
```

Converting the Character Variables into Numeric Variables for performing the Logistic Analysis and Viewing the Final Structure of the converted dataset for analysis.
```{r}
nonvars = c("PassengerId","Name","Ticket","Embarked","Cabin")
Titaniclog1 = Titaniclog1[,!(names(Titaniclog1) %in% nonvars)]
str(Titaniclog1)
```

Performing Sample Split,Train,Test for Dataset.
```{r}
library(caTools)
Sample_titlog1=sample.split(Titaniclog1,SplitRatio = 0.7)
Sample_titlog1
Train_titlog1=subset(Titaniclog1,Sample_titlog1=="TRUE")
Train_titlog1
Test_titlog1=subset(Titaniclog1,Sample_titlog1=="FALSE")
Test_titlog1
```
Building Model By using Binomial Family(Logistic Regression Analysis)
```{r}
#Building Model
Titaniclog1_eq=glm(Survived~.,Train_titlog1,family="binomial")
summary(Titaniclog1_eq)

```
Performing Prediction and Accuracy of the Test Data.
```{r}
##PREDICTION and ACCURACY
Test_titlog1_pred=predict(Titaniclog1_eq,Test_titlog1,type="response")
Test_titlog1_pred

T=table(actualvalue=Test_titlog1$Survived,predictedvalue=Test_titlog1_pred>0.62)
sum(diag(T))/sum(T)
```
ROCR Prediction and Performance Graphs.
```{r}
#ROCR
library(ROCR)
ROCRPred=prediction(Test_titlog1_pred,Test_titlog1$Survived)
ROCR_Perfor=performance(ROCRPred,"tpr","fpr")
plot(ROCR_Perfor,colorize=TRUE)
plot(ROCR_Perfor,colorize=TRUE,print.cutoffs.at=seq(0.1,by =0.1))

```

Plotting using GGPlot Concepts.
```{r}
##GGPLOT CONCEPTS
library(ggplot2)
library(ggridges)
library(ggExtra)
LT=dim(Train_titlog1)[1]
#Graph 1
Titaniclog1$Survived=as.factor(Titaniclog1$Survived)
ggplot(Titaniclog1,aes(x=Sex,y=Survived,col=Survived))+geom_jitter()+labs(title = "SURVIVAL ANALYSIS BETWEEN MALE AND FEMALE")
Titaniclog1$Survived=factor(Titaniclog1$Survived,levels=c(0,1))
summary(Titaniclog1$Survived)
#Graph 2
# Survival as a function of Pclass:
ggplot(data = Titaniclog1[1:LT,],aes(x=Pclass,fill=Survived))+geom_bar(position="fill")+ylab("Frequency")
#Graph 3
# Relationship between sex and survival:
ggplot(data=Titaniclog1[1:LT,],aes(x=Sex,fill=Survived))+geom_bar()
#Graph 4
# Survival as a function of age:
ggplot(data = Titaniclog1[!(is.na(Titaniclog1[1:LT,]$Age)),],aes(x=Age,fill=Survived))+geom_histogram(binwidth =3)

```

